Trends from 30-Year Observations of Downward Solar Irradiance in Thessaloniki, Greece

### 2024-01-02 MDPI_submission.Rmd
Commit 2024-01-02 19:12

<!-- \begin{figure}[h!] -->
<!--     \begin{adjustwidth}{-\extralength}{0cm} -->
<!--         {\centering  -->
<!--             \includegraphics[width=1\linewidth]{./images/SeasonalMTrendsTogether3-2}   % Seasonal from Monthly -->
<!--         } -->
<!--     \end{adjustwidth} -->
<!--     \caption{Time serries of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots). The black lines represent the linear trends, (\textbf{a}--\textbf{c}) winter, (\textbf{d}--\textbf{f}) spring, (\textbf{g}--\textbf{i}) summer, (\textbf{j}--\textbf{l}) autumn, and also (\textbf{a}, \textbf{d}, \textbf{g}, \textbf{j}) all-skies, (\textbf{b}, \textbf{e}, \textbf{h}, \textbf{k}) clear-skies and (\textbf{c}, \textbf{f}, \textbf{i}, \textbf{l}) cloudy-skies.}\label{fig:seasonalALL} -->
<!-- \end{figure} -->

\vspace{+100pt}

>>>>

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \includegraphics[width=1\linewidth]{./images/SeasonalMTrendsTogether3-2}   % Seasonal from Monthly
        }
    \end{adjustwidth}
    \caption{Time serries of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots). The black lines represent the linear trends, (\textbf{a}--\textbf{c}) winter, (\textbf{d}--\textbf{f}) spring, (\textbf{g}--\textbf{i}) summer, (\textbf{j}--\textbf{l}) autumn, and also (\textbf{a}, \textbf{d}, \textbf{g}, \textbf{j}) all-skies, (\textbf{b}, \textbf{e}, \textbf{h}, \textbf{k}) clear-skies and (\textbf{c}, \textbf{f}, \textbf{i}, \textbf{l}) cloudy-skies.}\label{fig:seasonalALL}
\end{figure}

### 2024-01-02 MDPI_submission.tex
Commit 2024-01-02 19:12

>>>>

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \includegraphics[width=1\linewidth]{./images/SeasonalMTrendsTogether3-2}   % Seasonal from Monthly
        }
    \end{adjustwidth}
    \caption{Time serries of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots). The black lines represent the linear trends, (\textbf{a}--\textbf{c}) winter, (\textbf{d}--\textbf{f}) spring, (\textbf{g}--\textbf{i}) summer, (\textbf{j}--\textbf{l}) autumn, and also (\textbf{a}, \textbf{d}, \textbf{g}, \textbf{j}) all-skies, (\textbf{b}, \textbf{e}, \textbf{h}, \textbf{k}) clear-skies and (\textbf{c}, \textbf{f}, \textbf{i}, \textbf{l}) cloudy-skies.}\label{fig:seasonalALL}
\end{figure}
